Automatic Matching of Bullet Lands

### 2016-01-05 imaging-paper.Rnw
forest-tree image

\begin{figure}[hbtp]
  \centering
<<tree:forest, echo=FALSE, fig.width=5, fig.height=2.5, out.width='.6\\textwidth', warning = FALSE>>=
predm <- melt(bstats, measure.var=c("pred", "forest"))
levels(predm$variable) <- c("Tree", "Forest")
predm$match <- c("KNM", "KM")[as.numeric(predm$match)+1]
qplot(data=predm, value, variable, geom="jitter", colour=match, shape=match) + theme_bw() + facet_grid(match~., labeller="label_both") +
    scale_colour_brewer(palette="Paired", labels=c("KNM", "KM")) +
  scale_shape_discrete(labels=c("KNM", "KM")) + ylab("") + 
  xlab("Predicted probability of a match") +
  theme(legend.position="none")

>>>>

\begin{figure}[hbtp]
  \centering
<<tree:forest, echo=FALSE, fig.width=5, fig.height=2.5, out.width='.6\\textwidth', warning = FALSE>>=
predm <- melt(bstats, measure.var=c("pred", "forest"))
levels(predm$variable) <- c("Tree", "Forest")
predm$match <- c("KNM", "KM")[as.numeric(predm$match)+1]
qplot(data=predm, value, match, geom="jitter", colour=match, shape=match) + theme_bw() + facet_grid(variable~.) +
    scale_colour_brewer(palette="Paired", labels=c("KNM", "KM")) +
  scale_shape_discrete(labels=c("KNM", "KM")) + ylab("") + 
  xlab("Predicted probability of a match") +
  theme(legend.position="none")
